\documentclass[11pt,a4paper]{report}

% Aberstwyth dissertation LaTeX Template
% Authors: Dr. Hannah Dee (hmd1@aber.ac.uk), Neil Taylor (nst@aber.ac.uk)
% This has been adapted from the Leeds Thesis template and the
% Group Project template for Computer Science in Aberystywth University.
%
% All comments and suggestions welcome.
%
% Template designed to be used with pdflatex: it may need alteration to
% run with a different LaTeX engine.
%
% Note - this is offered as a starting point for your work. You are not
% required to use this template and can choose to create your own document
% without it.

% To build document on the unix command line, run four commands:

% pdflatex dissertation
% bibtex dissertation
% pdflatex dissertation
% pdflatex dissertation

% you will end up with dissertation.pdf
\usepackage{mmp}
\usepackage{pdfpages}

% the following packages are used for citations - You only need to include one.
%
% Use the cite package if you are using the numeric style (e.g. IEEEannot).
% Use the natbib package if you are using the author-date style (e.g. authordate2annot).
% Only use one of these and comment out the other one.
% \usepackage{cite}
%\usepackage{natbib}

% Use the following to selectively exclude chapters
%\includeonly{cover,abstract,acknowledge,declare,chapter1,chapter2}

\begin{document}

% all of the include directives below refer to tex files
% so \include{cover} includes cover.tex - to change the content,
% edit the tex file

\pagenumbering{roman}

% This is the front page
\include{cover}

% Set up page numbering
\pagestyle{empty}

% declarations of originality
\include{declaration}

\include{acknowledgements} % Acknowledgements
\include{abstract}                 % Abstract

\pagenumbering{roman}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0 pt}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}

\tableofcontents
\newpage
\listoffigures
\newpage
\listoftables
\newpage

% Set up page numbering
\pagenumbering{arabic}

\setchapterheaderfooter

% include the chapters
\include{Chapter1/chapter1}
\include{Chapter2/chapter2}
\include{Chapter3/chapter3}
% add any additional chapters here

\setemptyheader
% start the appendix - sets up different numbering
\fancypagestyle{plain}{%
%\fancyhf{} % clear all header and footer fields
\fancyhead[L]{\textsl{Appendix\ \thechapter}}
\fancyhead[R]{\textsl{\leftmark}}}

\appendix
\fancyhead[L]{\textsl{Appendix\ \thechapter}}
\fancyhead[R]{\textsl{\leftmark}}
\fancyhead[C]{}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}

\fancyhead[L]{\textsl{Appendix\ \thechapter}}
\fancyhead[R]{\textsl{\leftmark}}
\fancyfoot[C]{{\thepage} of \pageref{LastPage}}

% include any appendices here
\include{Appendix1/appendix1}
\include{Appendix2/appendix2}
\include{Appendix3/appendix3}
\include{Appendix4/appendix4}
\include{Appendix5/appendix5}
\include{Appendix6/appendix6}
\include{Appendix7/appendix7}
\include{Appendix8/appendix8}

\fancypagestyle{plain}{%
   \fancyhead{} %[C]{Annotated Bibliography}
   \fancyfoot[C]{{\thepage} of \pageref{LastPage}} % except the center
   \renewcommand{\headrulewidth}{0pt}
   \renewcommand{\footrulewidth}{0pt}
}

\setemptyheader

% the following line is included so that the bibliography is also shown in the table of contents. There is the possibility that this is added to the previous page for the bibliography. To address this, a newline is added so that it appears on the first page for the bibliography.
\addcontentsline{toc}{chapter}{Bibliography} % Adds References to contents page

\begin{thebibliography}{1}

\bibitem{1} Qwizdom, “Qwizdom homepage,” 2018. [Online] Available: https://qwizdom.com/, [Accessed: Apr. 9, 2018].

  Qwizdom is the tool currently used by the univeristy and will be replaced with this project.

\bibitem{2} Google Sign-In, "Google Identity homepage", 2018. [Online] Available: https://developers.google.com/identity/, [Accessed: Apr. 10, 2018].

  Google Sign-In is a secure authentication system that reduces the burden of login for your users, by enabling them
  to sign in with their Google account. The same account they already use with Gmail, Play, Google+, and other Google services.

\bibitem{3} Java Programming Language, "Java homepage", 2018. [Online] Available:
  https://docs.oracle.com/javase/8/docs/technotes/guides/language/index.html, [Accessed: Apr. 11, 2018].

  The Java™ Programming Language is a general-purpose, concurrent, strongly typed, class-based object-oriented language.
  It is normally compiled to the bytecode instruction set and binary format defined in the Java Virtual Machine Specification.

\bibitem{4} Android, "Android homepage", 2018. [Online] Available: https://www.android.com/, [Accessed: Apr. 11, 2018].

  Android is a mobile operating system developed by Google.

\bibitem{5} iOS, "Apple homepage", 2018. [Online] Available: https://www.apple.com/uk/ios/ios-11/, [Accessed: Apr. 11, 2018].

  iOS is a mobile operating system created and developed by Apple Inc.

\bibitem{6} React Native, "React Native homepage", 2018. [Online] Available: https://facebook.github.io/react-native/, [Accessed: Apr. 11, 2018].

  React Native lets you build mobile apps for both iOS and Android using only JavaScript.

\bibitem{7} JavaScript Programming Language, "JavaScript Mozilla docs", 2018. [Online]
  Available: https://developer.mozilla.org/bm/docs/Web/JavaScript, [Accessed: Apr. 11, 2018].

  JavaScript is a lightweight, interpreted, programming language, best known for being the scripting
  language of the web.

\bibitem{8} React, "React homepage", 2018. [Online] Available: https://reactjs.org/, [Accessed: Apr. 11, 2018].

  A JavaScript library for building user interfaces.

\bibitem{9} Angular, "Angular homepage", 2018. [Online] Available: https://angular.io/, [Accessed: Apr. 11, 2018].

  Angular is a TypeScript-based front end development framework supported by Google.

\bibitem{10} TypeScript Programming Language, "TypeScript homepage", 2018. [Online] Available: https://www.typescriptlang.org/, [Accessed: Apr. 11, 2018].

  TypeScript is a typed superset of JavaScript that compiles to plain JavaScript.

  % 11 - 16
\bibitem{flask} Python Flask, "Flask homepage", 2018. [Online] Available: http://flask.pocoo.org/, [Accessed: Apr. 25, 2018].

  Flask is a micro web development framework for Python. It was considered as one of the alternative approaches to develop
  the back end of the Quiz Tool.

\bibitem{mvc} T. Reebskaug, J. Coplien, "The DCI Architecture: A New Vision of Object-Oriented Programming", 2009.
  [Online] Available: https://www.artima.com/articles/dci\_vision.html, [Accessed: Apr. 25, 2018].

  MVC is an architectural pattern which can be used for developing web applications. It was considered as one of the approaches
  of developing the Quiz Tool as a web application.

\bibitem{spring} Spring MVC, "Spring.io docs", 2018. [Online] Available: https://docs.spring.io/spring/docs/current/spring-framework-reference/web.html\#mvc, [Accessed: Apr. 25, 2018].

  Spring Web MVC is a web development framework build on the Servlet API using Java. It was considered as one of the alternative approaches to develop
  the back end of the Quiz Tool.

\bibitem{asp} ASP.NET, "ASP homepage", 2018. [Online] Available: https://www.asp.net/, [Accessed: Apr. 25, 2018].

    ASP.NET is an MVC web development framework, allowing web applications to be developed using the C\# programming language.
    It was considered as one of the alternative approaches to develop the back end of the Quiz Tool.

\bibitem{laravel} Laravel, "Laravel homepage", 2018. [Online] Available: https://laravel.com/, [Accessed: Apr. 25, 2018].

    Laravel is a PHP web development framework, considered as one of the alternative approaches to develop the Quiz Tool.

\bibitem{ror} Ruby on Rails, "Ruby on Rails homepage", 2018. [Online] Available: http://rubyonrails.org/, [Accessed: Apr. 25, 2018].

    Ruby on Rails is a convention over configuration web development framework, allowing applications to be written in the Ruby programming
    language. It was considered as one of the alternative approaches to develop the back end of the Quiz Tool.
  %

\bibitem{11} I. Fette, A. Melnikov, "The WebSocket Protocol", [Online] Available: https://tools.ietf.org/html/rfc6455, [Accessed: Apr. 11, 2018].

  The WebSocket Protocol enables two-way communication between a client running untrusted code in a controlled environment to a remote host
  that has opted-in to communications from that code.

\bibitem{12} Socket.io, "Socket.io homepage", 2018. [Online] Available: https://socket.io/, [Accessed: Apr. 11, 2018].

  Socket.io is a JavaScript library enabling bidirectional event-based communication.

\bibitem{13} Chat Application Tutorial, "Socket.io homepage", 2018. [Online] Available: https://socket.io/get-started/chat/, [Accessed: Apr. 11, 2018].

  A Socket.io tutorial guiding the student in developing a basic chat application using Socket.io.

\bibitem{14} Tour of Heroes Tutorial, "Angular homepage", 2018. [Online] Available: https://angular.io/tutorial, [Accessed: Apr. 11, 2018].

  The Tour of Heroes tutorial covers the fundamentals of Angular, by building an app that helps staffing agency manage its stable of heroes.

\bibitem{15} Building Chat Application using MEAN Stack (Angular 4) and Socket.io, "djamware.com", 2018.
  [Online] Available: https://www.djamware.com/post/58e0d15280aca75cdc948e4e/building-chat-application-using-mean-stack-angular-4-and-socketio,
  [Accessed: Apr. 11, 2018].

  Step by step tutorial of building simple chat application using MEAN stack (Angular 4) and Socket.io.

\bibitem{16} J. Sermersheim, Ed. Novell, "Lightweight Directory Access Protocol (LDAP): The Protocol", [Online]
    Available: https://tools.ietf.org/html/rfc4511, [Accessed: Apr. 11, 2018].

    Aberystwyth University directory of users could be checked using the Bind operation
    to authenticate lecturers once they provide their email and password.

\bibitem{17} Microsoft PowerPoint, "products.office.com", 2018. [Online] Available: https://products.office.com/en-gb/powerpoint, [Accessed: Apr. 11, 2018].

  A proprietary tool owned by Microsoft to create presentations.

\bibitem{18} MEAN stack, [Online] Available: https://github.com/linnovate/mean, [Accessed: Apr. 11, 2018].

    The MEAN stack uses Mongo, Express, Angular(4) and Node for simple and scalable fullstack js applications.

\bibitem{19} Docker, "Docker homepage", [Online] Available: https://www.docker.com/, [Accessed: Apr. 11, 2018].

    Docker allows app to be containerised and run on multiple hosts in the same fashion.

\bibitem{20} docker-compose, "docker-compose homepage", [Online] Available: https://docs.docker.com/compose/, [Accessed: Apr. 11, 2018].

    Compose is a tool for defining and running multi-container Docker applications.

\bibitem{21}  M. O\'Gara, "Ben Golub, Who Sold Gluster to Red Hat, Now Running dotCloud", 26th July 2013.
  [Online] Available: http://maureenogara.sys-con.com/node/2747331, [Accessed: Apr. 11, 2018].

  A journal article mentioning what Docker does.

\bibitem{22} LXC, "LXC", [Online] Available: https://wiki.debian.org/LXC, [Accessed: Apr. 11, 2018].

  Linux Containers (LXC) provide a Free Software virtualization system for computers running GNU/Linux. They are inappropriate
  for the task at hand, as they do not allow running docker-compose due to the lack of system permissions.

\bibitem{23} Jenkins, "Jenkins homepage", [Online] Available: https://jenkins.io/, [Accessed: Apr. 11, 2018].

  Jenkins is an industry proven automation tool. It is typically deployed
  on premises as a Java web application and gives developers more control over the build agents compared to its
  competitors.

\bibitem{24} Amazon Web Services, "AWS homepage", [Online] Available: https://aws.amazon.com/, [Accessed: Apr. 11, 2018].

  AWS provides cloud computing plaftoms to individuals, companies and governments. The production environment of Quiz Tool is
  hosted on AWS.

\bibitem{25} GitHub, "Student Developer Pack", [Online] Available: https://education.github.com/pack, [Accessed: Apr. 11, 2018].

  GitHub partners with top companies to allow students gain experience with real world tools. It funded the production
  environment hosting on AWS of the Quiz Tool.

\bibitem{26} Circle CI, "Circle CI  homepage", [Online] Available: https://circleci.com/, [Accessed: Apr. 12, 2018].

  Circle CI is very similar to Travis, but it allows a certain amount of free build hours per month for private
  repositories.

\bibitem{27} Travis, "Travis homepage", [Online] Available: https://travis-ci.org/, [Accessed: Apr. 12, 2018].

  Travis is a popular continuos integration tool hosted typically on an external cloud. Free to use for open source
  projects.

\bibitem{28} M. Shahin, M. Ali Babar, and L. Zhu, "Continuous Integration, Delivery and Deployment: A Systematic Review on
    Approaches, Tools, Challenges and Practices", 2017, [Online] Available: https://arxiv.org/pdf/1703.07019.pdf, [Accessed: Apr. 12, 2018].

    This paper describes what continuos integration and delivery are.

\bibitem{facebook} Facebook login, "developers.facebook.com", [Online] Available: https://developers.facebook.com/docs/facebook-login, [Accessed: Apr. 25, 2018].

  Facebook Single Sign On provides a secure, fast and convenient way for people to log into applications using their Facebook accounts.
  It was considered as one of the Single Sign On providers, before Google was chosen.

\bibitem{twitter} Sign in with Twitter, "dev.twitter.com", [Online] Available: https://dev.twitter.com/web/sign-in, [Accessed: Apr. 25, 2018].

  Twitter Single Sign On provides a secure, fast and convenient way for people to log into applications using their Twitter accounts.
  It was considered as one of the Single Sign On providers, before Google was chosen.

\bibitem{29} Git, “Git homepage,” 2018, [Online] Available: https://git-scm.com/, [Accessed: Apr. 12, 2018].

    Version control system used for the Quiz Tool development.

\bibitem{30} GitHub, Inc., “GitHub homepage,” 2018, [Online] Available: http://github.com/, [Accessed: Apr. 12, 2018].

    A popular version control web hosting offering private repositories to students. Code will be stored there and checkout by CI for
    testing and deployment.

\bibitem{31} Git Feature Branch Workflow, [Online] Available: https://www.atlassian.com/git/tutorials/comparing-workflows/feature-branch-workflow,
  [Accessed: Apr. 12, 2018].

    Each issue has an associated feature branch, and code necessary to develop the issue is commited to the appropriate feature branch.
    Then a pull request is made between the feature branch and development/master, and once all tests pass the feature branch can
    be merged to development/master.

\bibitem{32} ZenHub, "ZenHub homepage", [Online] Available: https://www.zenhub.com/, [Accessed: Apr. 12, 2018].

    ZenHub is an agile project management chrome extension for GitHub. It provides the ability to assign points
    to issues, create epics, provides velocity tracing burndown charts for milestones, and a Kanban board to
    better manage work at hand.

\bibitem{33} Google Sheets, "Google docs homepage", [Online] Available: https://www.google.co.uk/sheets/about/, [Accessed: Apr. 12, 2018].

  A SaaS tool for creating spreadsheets owned by Google. A spreadsheet has been used to track time commitment on day to day basis during
  the development of the Quiz Tool.

\bibitem{34} nginx, "nginx homepage", [Online] Available: https://www.nginx.com/, [Accessed: Apr. 12, 2018].

  Nginx is a web server which is used as a reverse proxy in the Quiz Tool.

\bibitem{35} avatsaev, "Dockerized Angular 4 App (with Angular CLI)", [Online] Available: https://github.com/avatsaev/angular4-docker-example, [Accessed: Apr. 12, 2018].

    The starting point of the client side of the Quiz Tool.

\bibitem{36} mongo, "mongo official docker repository", [Online] Available: https://hub.docker.com/\_/mongo/, [Accessed: Apr. 12, 2018].

    The official docker hub repository of MongoDB. The image is used by the Quiz Tool in both production and development.

\bibitem{37} What Is AWS Elastic Beanstalk, "AWS docs", [Online] Available: https://docs.aws.amazon.com/elasticbeanstalk/latest/dg/Welcome.html, [Accessed: Apr. 13, 2018].

    The Quiz Tool is deployed to AWS Elastic Beanstalk production environment.

\bibitem{38} Multicontainer Docker Environments, "AWS docs", [Online] Available: https://docs.aws.amazon.com/elasticbeanstalk/latest/dg/create\_deploy\_docker\_ecs.html, [Accessed: Apr. 13, 2018].

    The Multicontainer AWS Elastic Beanstalk is what actually orchestrates Docker containers in production.

\bibitem{39} Amazon EC2, "EC2 homepage", [Online] Available: https://aws.amazon.com/ec2/, [Accessed: Apr. 13, 2018].

    Amazon Elastic Compute Cloud (Amazon EC2) is a web service that provides secure, resizable compute capacity in the cloud. It is designed to make web-scale cloud computing easier for developers.

\bibitem{40} Amazon ECS, "ECS homepage", [Online] Available: https://aws.amazon.com/ecs/, [Accessed: Apr. 13, 2018].

    Amazon Elastic Container Service stores Docker images of the Quiz Tool tagged and ready for deployment into production.

\bibitem{41} How to setup Elastic Beanstalk Deployment, "circleci forum", [Online] Available: https://discuss.circleci.com/t/how-to-setup-elastic-beanstalk-deployment/6154/4, [Accessed: Apr. 13, 2018].

    The forum post shows an example of an AWS deployment script which was adapted for Quiz Tool deployment.

\bibitem{42} Settings to deploy to AWS Elastic Beanstalk on CircleCi (EB Cli 3) , "gist", [Online] Available: https://gist.github.com/RobertoSchneiders/9e0e73e836a80d53a21e, [Accessed: Apr. 13, 2018].

    The gist post shows an example of an AWS deployment script which was adapted for Quiz Tool deployment.

\bibitem{43} Materialize CSS, "Materialize homepage", [Online] Available: http://materializecss.com/, [Accessed: Apr. 14, 2018].

    The CSS framework used in the development of the Quiz Tool.

\bibitem{44} JSON Web Token, "JWT standard", [Online] Available: https://tools.ietf.org/html/rfc7519, [Accessed: Apr. 14, 2018].

  JSON Web Tokens are an open, industry standard RFC 7519 method for representing claims securely between two parties. Quiz Tool
  uses JWT tokens during authorisation.

\bibitem{45} passport.js, "passport.js homepage", [Online] Available: http://www.passportjs.org/, [Accessed: Apr. 14, 2018].

  Passport is an authentication middleware for Node.js used during Quiz Tool authentication.

\bibitem{46} passport-google-oauth, "passport-google-oauth github page", [Online] Available: https://github.com/jaredhanson/passport-google-oauth, [Accessed: Apr. 14, 2018].

  Passport middleware Google authentication strategy used in Quiz Tool.

\bibitem{47} OAuth2, "OAuth 2.0 Authorization Framework", [Online] Available: https://tools.ietf.org/html/rfc6749, [Accessed: Apr. 14, 2018].

  The OAuth 2.0 authorization framework enables a third-party application to obtain limited access to a resource stored on a
  different server. Quiz Tool uses it to authenticate lecturers using their Google credentials.

\bibitem{48} mongoose, "mongoose homepage", [Online] Available: http://mongoosejs.com/, [Accessed: Apr. 14, 2018].

    Mongoose provides a schema-based solution to model data in applications using MongoDB.

\bibitem{49} Binary JSON, "BSON homepage", [Online] Available: http://bsonspec.org/, [Accessed: Apr. 15, 2018].

    A binary-encoded serialization of JSON-like documents. Quiz Tool uses BSON as datatype of files persisted in MongoDB.

\bibitem{50} GridFS, "mongo docs", [Online] Available: https://docs.mongodb.com/manual/core/gridfs/, [Accessed: Apr. 15, 2018].

    A convention for storing large files in a MongoDB database.

\bibitem{51} ng2-file-upload, "ng2-file-upload homepage", [Online] Available: https://valor-software.com/ng2-file-upload/, [Accessed: Apr. 15, 2018].

    Library simplifying file upload from Angular applications.

\bibitem{52} pdf-extract, "pdf-extract github repository", [Online] Available: https://github.com/nisaacson/pdf-extract, [Accessed: Apr. 15, 2018].

    Node PDF is a set of tools that takes in PDF files and converts them to usable formats for data processing.

\bibitem{53} scissors, "scissors github repository", [Online] Available: https://github.com/tcr/scissors, [Accessed: Apr. 15, 2018].

    PDF manipulation in Node.js, based on PDFTK. This library has been initially used to extract PNG images from PDF slides.

\bibitem{54} The Base16, Base32, and Base64 Data Encodings, "Base64 standard", [Online] Available: https://tools.ietf.org/html/rfc4648, [Accessed: Apr. 15, 2018].

    Base64 is a binary-to-text encoding scheme used in the Quiz Tool to broadcast image slides to all the students.

\bibitem{55} PDFtk Server, "PDFtk homepage", [Online] Available: https://www.pdflabs.com/tools/pdftk-server/, [Accessed: Apr. 15, 2018].

    PDFtk is a command line utility for working with PDF files. It is used by the Quiz Tool internally when PNG images are extracted
    from PDF presentations uploaded by lecturers.

\bibitem{56} node-pdf2img, "node-pdf2img GitHub repository", [Online] Available: https://github.com/fitraditya/node-pdf2img, [Accessed: Apr. 15, 2018].

    A NodeJS module for converting pdf into image files.

\bibitem{57} jsPDF, "jsPDF GitHub repository", [Online] Available: https://github.com/MrRio/jsPDF, [Accessed: Apr. 16, 2018].

    Client-side JavaScript PDF generator, used for report generation in the Quiz Tool.

\bibitem{58} jsonschema, "jsonschema GitHub repository", [Online] Available: https://github.com/tdegrunt/jsonschema, [Accessed: Apr. 17, 2018].

    JSON Schema validator is used to make sure JSON send together with certain routes to the back end of the Quiz Tool is valid.

\bibitem{59} mocha, "mocha homepage", [Online] Available: https://mochajs.org/, [Accessed: Apr. 17, 2018].

    Mocha is a test framefork for Node.js, it is used in back end unit testing of the Quiz Tool.

\bibitem{60} chai, "chai homepage", [Online] Available: http://www.chaijs.com/, [Accessed: Apr. 17, 2018].

    Chai is an assertion library used in the back end unit testing of the Quiz Tool.

\bibitem{61} chai-http, "chai-http GitHub repository", [Online] Available: https://github.com/chaijs/chai-http, [Accessed: Apr. 17, 2018].

    Chai-http is an integration testing library allowing creation of tests which can call endpoints exposed by the Node.js
    applications.

\bibitem{62} S. Zaza, "Test a Node RESTful API with Mocha and Chai", [Online] Available: https://scotch.io/tutorials/test-a-node-restful-api-with-mocha-and-chai, [Accessed: Apr. 17, 2018].

    Tutorial explaining how to incorporate automated testing in a Node.js project. The tutorial was the basis of the
    server side unit tests of the Quiz Tool.

\bibitem{63} Karma, "Karma GitHub repository", [Online] Available: https://karma-runner.github.io/2.0/index.html, [Accessed: Apr. 18, 2018].

    Karma is the test runner which comes with Angular, and has been used for the front end unit tests of the Quiz Tool.

\bibitem{64} Jasmine, "Jasmine GitHub repository", [Online] Available: https://jasmine.github.io/, [Accessed: Apr. 18, 2018].

    Jasmine is a testing framework for JavaScript. It comes with Angular and is used for front end unit testing of the Quiz Tool.

\bibitem{65} PhantomJS, "PhantomJS homepage", [Online] Available: http://phantomjs.org/, [Accessed: Apr. 18, 2018].

  PhantomJS headless web browser is spin up by Karma during front end unit tests.

\bibitem{66} Selenium, "Selenium homepage", [Online] Available: https://www.seleniumhq.org/, [Accessed: Apr. 18, 2018].

  Selenium is a tool which automates browsers. It has been used to driver browser interactions during integration/end-to-end tests.

\bibitem{67} Selenium-Grid, "Selenium homepage", [Online] Available: https://www.seleniumhq.org/docs/07\_selenium\_grid.jsp, [Accessed: Apr. 18, 2018].

  Selenium-Grid can be used to run selenium tests on multiple web browers in parallel.

\bibitem{68} Getting Started with Docker Compose, "docker-selenium GutHub repository", [Online] Available: https://github.com/SeleniumHQ/docker-selenium/wiki/Getting-Started-with-Docker-Compose, [Accessed: Apr. 18, 2018].

  A step-by-step introduction to using the official Selenium Docker images using a basic hub/node configuration and docker-compose.

\bibitem{69} selenium-webdriver, "Selenium GutHub repository", [Online] Available: https://github.com/SeleniumHQ/selenium/tree/master/javascript/node/selenium-webdriver, [Accessed: Apr. 18, 2018].

  The selenium-driver can be used to use Selenium to automate web browser automation. The JavaScript implementation
  has been added to the tester container running integration tests of the Quiz Tool.




\end{thebibliography}

\end{document}
